---
title: "INDOMIE FACEBOOK PAGE DYNAMICS REPORT"
author: "ISAAC OWUSU AKOWUAH"
date: "January 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**MULTIPRO PRIVATE LIMITED** is a sales and marketing company concerned with noodle, kellogs, pasta and chinchin products. As part of their digital marketing approach, they host a Facebook page to engage their customers and also target consumers. This seeks to analyse their data generated on their page from January 2017 to December 2017.
```{r cars, echo= TRUE, message=FALSE}
##############
######Packages Required
#############
library("Rfacebook")
library("stringr")
library("reshape2")
library("ggplot2")
library("scales")
#library("cowplot")
###########
####Loading Scrapped Data
load("Yummie.RData")
load("Indomie_Ghana.RData")
```

### 1. What is the trend of likes, comments and shares for Indomie_Ghana?

```{r cas, echo= TRUE, message=FALSE}
format.facebook.date<-function(datestring){
  date<-as.POSIXct(datestring,format="%Y-%m-%dT%H:%M:%S+0000",tz="GMT")
}

aggregate.metric<-function(metric){
  m<-aggregate(Indomie_Ghana[[paste0(metric,"_count")]],list(month=Indomie_Ghana$month),mean)
  m$month<-as.Date(paste0(m$month,"-15"))
  m$metric<-metric
  return(m)
}

Indomie_Ghana$datetime<-format.facebook.date(Indomie_Ghana$created_time)
Indomie_Ghana$month<-format(Indomie_Ghana$datetime,"%Y-%m")
df.List<-lapply(c("likes","comments","shares"),aggregate.metric)
df<-do.call(rbind,df.List)


t<-ggplot(df,aes(x=month,y=x,group=metric))+geom_line(aes(color=metric))+scale_x_date(date_breaks = "months",labels = date_format("%m"))+theme_bw()+theme(axis.title.x = element_blank())+labs(y="Average count per post",title=("INDOMIE MONTHLY AVERAGE PAGE REACTION TREND"),caption="Data Source: Facebook_Indomie_Ghana")+ylim(0,6000)
t
```

### 2. What is the likes, comments and shares trend for Yummie?
```{r ca, echo= TRUE, message=FALSE}
format.facebook.date<-function(datestring){
  date<-as.POSIXct(datestring,format="%Y-%m-%dT%H:%M:%S+0000",tz="GMT")
}

aggregate.metric<-function(metric){
  m<-aggregate(Yummie[[paste0(metric,"_count")]],list(month=Yummie$month),mean)
  m$month<-as.Date(paste0(m$month,"-15"))
  m$metric<-metric
  return(m)
}

Yummie$datetime<-format.facebook.date(Yummie$created_time)
Yummie$month<-format(Yummie$datetime,"%Y-%m")
df.List<-lapply(c("likes","comments","shares"),aggregate.metric)
df<-do.call(rbind,df.List)

n<-ggplot(df,aes(x=month,y=x,group=metric))+geom_line(aes(color=metric))+scale_x_date(date_breaks = "months",labels = date_format("%m"))+theme_bw()+theme(axis.title.x = element_blank())+labs(y="Average count per post",title=("YUMMIE MONTHLY AVERAGE PAGE REACTION TREND"),caption="Data Source: Facebook_Yummie")
n

#plot_grid(t,n, labels = "AUTO")
```

### 3. Which post generated maximum likes count?
```{r caTT, echo= TRUE, message=FALSE}
Indomie_Ghana[which.max(Indomie_Ghana$likes_count),]
```

### 4 .Which post generated maximum likes count greater than 10000?
```{r caTTji, echo= TRUE, message=FALSE}
which(Indomie_Ghana$likes_count>=10000)
Indomie_Ghana[244,]
Indomie_Ghana[245,]
Indomie_Ghana[246,]
Indomie_Ghana[247,]
```

### 5. Which post generated maximum comments count?
```{r caTTer, echo= TRUE, message=FALSE}
Indomie_Ghana[which.max(Indomie_Ghana$comments_count),]
```

### 6. Which post generated maximum shares count?
```{r caTTergh, echo= TRUE, message=FALSE}
Indomie_Ghana[which.max(Indomie_Ghana$shares_count),]
```
### 7. What post by competitor generated many likes count?
```{r TT, echo= TRUE, message=FALSE}
Yummie[which.max(Yummie$likes_count),]
```
### 8. What post by competitor generated many comments count?
```{r TTq, echo= TRUE, message=FALSE}
Yummie[which.max(Yummie$comments_count),]
```
### 9. What post by competitor generated many shares count?
```{r TTqr, echo= TRUE, message=FALSE}
Yummie[which.max(Yummie$shares_count),]
```

### 10. What post type is most observed on Indomie Page?
```{r TTY, echo= TRUE, message=FALSE}
names(Yummie)[5]<-"Post_Type"
names(Indomie_Ghana)[5]<-"Post_Type"
Indomieplot<-ggplot(Indomie_Ghana,aes(x=Post_Type,fill=Post_Type))+geom_bar(position = "dodge")
Indomieplot+ labs(title="INDOMIE POST TYPE", y="Number of Posts", x="Post Type", caption="Data Source: Facebook_Indomie_Ghana")
```

### 11. How does Indomie Post compare with the competitor Yummie post?

```{r TTP, echo= TRUE, message=FALSE}
index<-c(2,4,5,8,9,10)
data<-rbind(Indomie_Ghana[,index],Yummie[,index])
names(data)[1]<-"Page"
ggplot(data,aes(x=Post_Type,fill=Page))+geom_bar(position = "dodge")+ labs(title="INDOMIE AND YUMMIE POST TYPE COMPARISON", y="Number of Posts", x="Post Type", caption="Data Source: Facebook")
```

### 12. What is the trend of Engagement of Indomie and Yummie for the year?
**Engagement is the total likes, comments and shares count**
```{r TTD, echo= TRUE, message=FALSE}
Noodle<-rbind(Indomie_Ghana,Yummie)
Noodle$Engagement<-(Noodle$likes_count+Noodle$comments_count+Noodle$shares_count)
ggplot(subset(Noodle,Noodle$from_name %in% c("Indomie Ghana","Yum-mie")),aes(x=as.Date(Noodle$created_time),y=Noodle$Engagement,color=Noodle$from_name))+geom_step()+labs(caption = "(Based on Facebook Data  from JAN 2017 - DEC 2017)",title = "POST ENGAGEMENT OVER TIME ",x="Post Date",y="Engagement",colour="NOODLE BRAND")
```

### 13. How likely is Yummie to post ahead of Indomie**
```{r TTX, echo= TRUE, message=FALSE}
(nrow(Yummie)/nrow(Indomie_Ghana))
```
### 14. What is the percentage difference in post by Indomie and Yummie?
```{r TTF, echo= TRUE, message=FALSE}
a=nrow(Yummie)/(nrow(Yummie)+nrow(Indomie_Ghana))*100

b=nrow(Indomie_Ghana)/(nrow(Yummie)+nrow(Indomie_Ghana))*100

a-b
```

### 15. What is the comparative post per month for Indomie and Yummie?
```{r HHG, echo= TRUE, message=FALSE}
Noodle$Month<-as.Date(Noodle$created_time)
Noodle$mon<-as.numeric(format(Noodle$Month,format="%m"))
save(Noodle,file ="Noodle.RData")
Noodle$mon[Noodle$mon==1]<-"Jan"
Noodle$mon[Noodle$mon==2]<-"Feb"
Noodle$mon[Noodle$mon==3]<-"Mar"
Noodle$mon[Noodle$mon==4]<-"Apr"
Noodle$mon[Noodle$mon==5]<-"May"
Noodle$mon[Noodle$mon==6]<-"Jun"
Noodle$mon[Noodle$mon==7]<-"Jul"
Noodle$mon[Noodle$mon==8]<-"Aug"
Noodle$mon[Noodle$mon==9]<-"Sep"
Noodle$mon[Noodle$mon==10]<-"Oct"
Noodle$mon[Noodle$mon==11]<-"Nov"
Noodle$mon[Noodle$mon==12]<-"Dec"
names(Noodle)[2]<-"Noodle_Page"
Noodle$mon<-factor(Noodle$mon,levels = c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
ggplot(Noodle,aes(x=mon,fill=Noodle_Page))+geom_bar(position = "dodge")+scale_x_discrete(limits=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))+labs(title="INDOMIE AND YUMMIE MONTHLY POST COMPARISON", y="Number of Posts", x="Month", caption="Data Source: Facebook")
```

### 16. What is the average post per month for Indomie and Yummie?
```{r HHDF, echo= TRUE, message=FALSE}
#Yummie average post per month
nrow(Yummie)/12
#Indomie average post per month
nrow(Indomie_Ghana)/12
dat = data.frame(count=c(26, 36), Noodle_Brand=c("Indomie_Ghana", "Yummie"))

# Add addition columns, needed for drawing with geom_rect.
dat$fraction = dat$count / sum(dat$count)
dat = dat[order(dat$fraction), ]
dat$ymax = cumsum(dat$fraction)
dat$ymin = c(0, head(dat$ymax, n=-1))

# Make the plot
p1 = ggplot(dat, aes(fill=Noodle_Brand, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
  geom_rect() +
  coord_polar(theta="y") +
  xlim(c(0, 4)) +
  theme(panel.grid=element_blank()) +
  theme(axis.text=element_blank()) +
  theme(axis.ticks=element_blank()) +
  labs(title="AVERAGE POST PER MONTH")
p1
```


